---
title: "Untitled"
author: "Gabriel Vayá"
date: "2023-12-13"
output: 
  pdf_document: 
    toc: true
    toc_depth: 3
    number_sections: true
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Clear plots
if(!is.null(dev.list())) dev.off()

# Clean workspace
rm(list=ls())

library(car)
library(MASS)
library(missMDA)
library(visdat)
library(FactoMineR)
library(chemometrics)
library(corrplot)
library(naniar)
```

```{r}
setwd("/Users/gabrielvayaabad/Desktop/MDS/SIM/Assignment 2")
df <- read.csv2("WA_Fn-UseC_-Telco-Customer-Churn.csv")

df$MonthlyCharges <- as.numeric(df$MonthlyCharges)
df$TotalCharges <- as.numeric(df$TotalCharges)
df[sapply(df, is.character)] <- lapply(df[sapply(df, is.character)], as.factor)
df$SeniorCitizen <- as.factor(df$SeniorCitizen)
df$customerID <- as.character(df$customerID)
levels(df$SeniorCitizen) <- c("No","Yes")
```


#DataPreparation

#Deduplication
```{r}
dup <- which(duplicated(df)) #No duplicate rows
```

#Missing Values
```{r}
df[is.na(df$TotalCharges),]

mcar_test(df) #p-value is 0 -> not random
df$tenure[is.na(df$TotalCharges)]
#Impute with 0
df$TotalCharges[is.na(df$TotalCharges)] <- 0
sum(is.na(df))
```

#MultivariateOutliers
```{r}
num <- which(sapply(df,is.numeric))

res.mout <- Moutlier(df[,num],quantile=0.99,plot=F)
length(which(res.mout$md > res.mout$cutoff));
m.out <- which(res.mout$md > res.mout$cutoff)
plot(res.mout$md, res.mout$rd)

#df <- df[-m.out,] 
```
Maybe because there is continuity in the distribution we don't take them out (see plot)

#EDA

#gender
```{r}
sum(is.na(df$gender))
barplot(table(df$gender),col='lightblue')
```

#SeniorCitizen
```{r}
sum(is.na(df$SeniorCitizen))
barplot(table(df$SeniorCitizen),col='lightblue')
```

#Partner
```{r}
sum(is.na(df$Partner))
barplot(table(df$Partner),col='lightblue')
```

#Dependents
```{r}
sum(is.na(df$Dependents))
barplot(table(df$Dependents),col='lightblue')
```

#tenure
```{r}
sum(is.na(df$tenure))
hist(df$tenure,freq=F,15)
mm <- mean(df$tenure,na.rm=T);ss <- sd(df$tenure,na.rm=T);mm;ss
curve(dnorm(x,mm,ss),col="red",add=T)
shapiro.test(df$tenure)
Boxplot(df$tenure,range=3,id=list(n=Inf,labels=rownames(df)))
exoutl <- as.integer(Boxplot(df$tenure,range=6,id=list(n=Inf,labels=rownames(df))))
```

#PhoneService
```{r}
sum(is.na(df$PhoneService))
barplot(table(df$PhoneService),col='lightblue')
```

#MultipleLines
```{r}
sum(is.na(df$MultipleLines))
barplot(table(df$MultipleLines),col='lightblue')
```

#InternetService
```{r}
sum(is.na(df$InternetService))
barplot(table(df$InternetService),col='lightblue')
```

#OnlineSecurity
```{r}
sum(is.na(df$OnlineSecurity))
barplot(table(df$OnlineSecurity),col='lightblue')
```

#OnlineBackup
```{r}
sum(is.na(df$OnlineBackup))
barplot(table(df$OnlineBackup),col='lightblue')
```

#DeviceProtection
```{r}
sum(is.na(df$DeviceProtection))
barplot(table(df$DeviceProtection),col='lightblue')
```

#TechSupport
```{r}
sum(is.na(df$TechSupport))
barplot(table(df$TechSupport),col='lightblue')
```

#StreamingMovies
```{r}
sum(is.na(df$StreamingMovies))
barplot(table(df$StreamingMovies),col='lightblue')
```

#Contract
```{r}
sum(is.na(df$Contract))
barplot(table(df$Contract),col='lightblue')
```

#PaperlessBilling
```{r}
sum(is.na(df$PaperlessBilling))
barplot(table(df$PaperlessBilling),col='lightblue')
```

#PaymentMethod
```{r}
sum(is.na(df$PaymentMethod))
barplot(table(df$PaymentMethod),col='lightblue')
```

#MonthlyCharges
```{r}
sum(is.na(df$MonthlyCharges))
hist(df$MonthlyCharges,freq=F,15)
mm <- mean(df$MonthlyCharges,na.rm=T);ss <- sd(df$MonthlyCharges,na.rm=T);mm;ss
curve(dnorm(x,mm,ss),col="red",add=T)
shapiro.test(df$MonthlyCharges)
Boxplot(df$MonthlyCharges,range=3,id=list(n=Inf,labels=rownames(df)))
exoutl <- as.integer(Boxplot(df$MonthlyCharges,range=6,id=list(n=Inf,labels=rownames(df))))
```

#TotalCharges
```{r}
sum(is.na(df$TotalCharges)) #11 NA's
hist(df$TotalCharges,freq=F,15)
mm <- mean(df$TotalCharges,na.rm=T);ss <- sd(df$TotalCharges,na.rm=T);mm;ss
curve(dnorm(x,mm,ss),col="red",add=T)
shapiro.test(df$TotalCharges)
Boxplot(df$TotalCharges,range=3,id=list(n=Inf,labels=rownames(df)))
exoutl <- as.integer(Boxplot(df$TotalCharges,range=6,id=list(n=Inf,labels=rownames(df))))
```

#Target Variable: Churn
```{r}
sum(is.na(df$Churn))
barplot(table(df$Churn),col='lightblue')
```

#Profiling of target variable 
```{r}
catdes(df,21)
```


#
```{r}

```

